\section{Conferences}

{\large\textbf{Papers}} \vspace{.5em}
  \begin{bibenum}
    \item[] Kearney, M.W. (2018, May).
      \textit{A network-based approach to estimating political partisanship}.
      Paper accepted for the the 68th Annual International Communication Association conference in Prague, Czech Republic.
    \item[] Hall, J. A., Kearney, M. W., \& Xing, C. (2017, May).
      \textit{Two tests of social displacement through social media use}.
      Paper presented at the 67th Annual International Communication Association Convention in San Diego, CA.
    \item[] Warner, B. R., \& Kearney, M. W. (2017, Sep).
      \textit{No spillover: A longitudinal analysis of the effects of political communication online and off}.
      Paper presented at the 3rd Annual International Journal of Press/Politics Conference in Oxford, UK.
    \item[] Kearney, M. W., \& Webb, C. M. (2017, Sep).
      \textit{\#Politics: Using Twitter data to study public attitudes and public attention in event}.
      Paper presented at the 113th Annual American Political Science Association Meeting \& Exhibition in San Fransico, CA.
    \item[] Kearney, M. W. (2017, May).
      \href{https://mkearney.github.io/ica17/}{\textit{An introduction to rtweet: Collecting Twitter data}}.
      Paper presented at the 67th Annual International Communication Association Convention in San Diego, CA.
    \item[] Hall, J. A., Xing, C., \& Kearney, M. W. (2017, May).
      \textit{Two tests of social displacement through social media}.
      Paper presented at the 67th Annual International Communication Association Convention in San Diego, CA.
    \item[] Webb, C. M., \& Kearney, M. W. (2017, February).
      \textit{Statecraft or sacrifice? The domestic political dynamics of economic sanctions}.
      Paper presented at the 58th Annual International Studies Association Convention in Baltimore, MD.
    \item[] Kearney, M. W. (2016, April).
      \textit{The null effect of social media use on political participation}.
      Paper presented in the Political Communication Interest Group at the CSCA Annual Conference, Grand Rapids, MI.
    \item[] Kearney, M. W. (2016, April).
      \textit{Theoretical and empirical review of political discussion orientation scales}.
      Paper presented in the Political Communication Interest Group at the CSCA Annual Conference, Grand Rapids, MI.
    \item[] Kearney, M. W. \& Quenette, A. (2015, November).
      \textit{"Nationalizing" the 2014 midterm election: Effects of national news source on perceived candidate polarization}.
      Paper presented at the NCA 101st Annual Convention, Las Vegas, NV.
    \item[] Kearney, M. W. (2015, March).
      \textit{The long game: Political communication and modern longitudinal designs}.
      Paper presented at the CSCA Annual Conference, Madison, WI.
    \item[] Kearney, M. W. (2015, March).
      \textit{Emphasizing equivalent frames: Political polarization and information processing}.
      Paper presented at the CSCA Annual Conference, Madison, WI.\\
      {$\star$} Top paper panel
    \item[] Kearney, M. W. (2015, March).
      \textit{Young voters and the polarizing price of political engagement}.
      Paper presented at the CSCA Annual Conference, Madison, WI.
    \item[] Kearney, M. W. (2015, March).
      \textit{It's my party: The effects of polarizing party frames on information processing}.
      Paper presented at the CSCA Annual Conference, Madison, WI.
    \item[] Kearney, M. W. (2014, November).
      \textit{Old arguments, new Face[book]s: Analyzing political disagreement on Facebook}.
      Paper presented at the NCA 100th Annual Convention, Chicago, IL.
    \item[] Kearney, M. W. (2014, November).
      \textit{Yesterday's public opinion expression, today's status update: Interpersonal goals in Facebook political discussion}.
      Paper presented at the NCA 100th Annual Convention, Chicago, IL.
    \item[] Kearney, M. W. (2014, May).
      \textit{Agonistic politics and the democratic debate following 9/11}.
      Paper presented at the 16th Biennial RSA Conference, San Antonio, TX.
    \item[] Kearney, M. W. (2014, March).
      \textit{Civic or civic? An Empirical examination of democratic orientations and civic dialogue}.
      Paper presented at the Civic Dialogue and Leadership Conference, College Station, TX.
    \item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney, M. W. (2014, March).
      \textit{The next Facebook election: Evaluating political engagement and efficacy on Facebook during the 2012 presidential election}.
      Paper presented at the CSCA Annual Conference, Minneapolis, MN.\\
      {$\star$} Top student paper
    \item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney, M. W. (2013, November).
      \textit{Finding a role model on Facebook: Political candidates' use of Facebook and young women's political engagement}.
      Paper presented at the 99th NCA Annual Convention, Washington, D.C.
  \end{bibenum}

  \vspace{1.5em}
