\documentclass[11pt,letterpaper]{article}
\usepackage{iftex}
\usepackage{fontspec}
\setsansfont[Scale=1]{Latin Modern Roman}
\setmainfont
%  [Ligatures=TeX,
%   UprightFont={* Light},
%   ItalicFont={* Light Italic},
%   BoldFont={* Medium},
%   BoldItalicFont={* Medium Italic}]
  {Adobe Garamond Pro}

\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage{calc}
\reversemarginpar
\usepackage[paper=letterpaper,marginparwidth=1.1in,
marginparsep=0in,margin=.75in,
includemp]{geometry}
\usepackage[shortlabels]{enumitem}
\usepackage{color,hyperref}
\definecolor{blue}{rgb}{.0,.15,.55}
\hypersetup{colorlinks,breaklinks,
  linkcolor=blue,urlcolor=blue}
\usepackage{url}
\urlstyle{same}
\usepackage{microtype}

\makeatletter
\newlength{\bibhang}
\setlength{\bibhang}{1em}
\newlength{\bibsep}
{\@listi \global\bibsep\itemsep \global\advance\bibsep by\parsep}
\newlist{bibsection}{itemize}{3}
\setlist[bibsection]{label=,leftmargin=\bibhang,%
  itemindent=-\bibhang,
  itemsep=\bibsep,parsep=\z@,partopsep=0pt,
  topsep=0pt}
\newlist{bibenum}{enumerate}{3}
\setlist[bibenum]{label=,leftmargin=\bibhang,%
  itemindent=-\bibhang,
  itemsep=\bibsep,parsep=\z@,partopsep=0pt,
  topsep=0pt}
\let\oldendbibenum\endbibenum
\def\endbibenum{\oldendbibenum\vspace{-.6\baselineskip}}
\let\oldendbibsection\endbibsection
\def\endbibsection{\oldendbibsection\vspace{-.6\baselineskip}}
\makeatother

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
{0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}

\newcommand{\makeheading}[2][]%
{\hspace*{-\marginparsep minus \marginparwidth}%
  \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
    %{\huge \bfseries #2}\\[-.5\baselineskip]%
    {\Huge \bfseries \sffamily #2}\\[-.25\baselineskip]%
    \rule{\columnwidth}{.75pt}%
  \end{minipage}}

\renewcommand{\section}[1]{\pagebreak[3]%
  \vspace{1.5\baselineskip}%
  \phantomsection\addcontentsline{toc}{section}{#1}%
  \noindent\llap{\small\scshape\smash{\parbox[t]{\marginparwidth}{\hyphenpenalty=10000\raggedright #1}}}%
  \vspace{-\baselineskip}\par}

\newcommand*\fixendlist[1]{%
  \expandafter\let\csname preFixEndListend#1\expandafter\endcsname\csname end#1\endcsname
  \expandafter\def\csname end#1\endcsname{\csname preFixEndListend#1\endcsname\vspace{-0.6\baselineskip}}}

\let\originalItem\item
\newcommand*\fixouterlist[1]{%
  \expandafter\let\csname preFixOuterList#1\expandafter\endcsname\csname #1\endcsname
  \expandafter\def\csname #1\endcsname{\let\oldItem\item\def\item{\pagebreak[2]\oldItem}\csname preFixOuterList#1\endcsname}
  \expandafter\let\csname preFixOuterListend#1\expandafter\endcsname\csname end#1\endcsname
  \expandafter\def\csname end#1\endcsname{\let\item\oldItem\csname preFixOuterListend#1\endcsname}}
\newcommand*\fixinnerlist[1]{%
  \expandafter\let\csname preFixInnerList#1\expandafter\endcsname\csname #1\endcsname
  \expandafter\def\csname #1\endcsname{\let\oldItem\item\let\item\originalItem\csname preFixInnerList#1\endcsname}
  \expandafter\let\csname preFixInnerListend#1\expandafter\endcsname\csname end#1\endcsname
  \expandafter\def\csname end#1\endcsname{\csname preFixInnerListend#1\endcsname\let\item\oldItem}}

\newlist{outerlist}{itemize}{3}
\setlist[outerlist]{label=$\star$,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
\fixendlist{outerlist}
\fixouterlist{outerlist}

\newlist{innerlist}{itemize}{3}
\setlist[innerlist]{label=\enskip$\star$,leftmargin=*,parsep=0pt,itemsep=0pt,topsep=0pt,partopsep=0pt}
\fixinnerlist{innerlist}

\setlength{\parindent}{0in}

\providecommand*\emaillink[1]{\nolinkurl{#1}}
\providecommand*\email[1]{\href{mailto:#1}{\emaillink{#1}}}

\hyphenation{bio-mim-ic-ry bio-in-spi-ra-tion re-us-a-ble pro-vid-er Media-Wiki}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\makeheading{Michael W. Kearney}

\section{Contact Information}

\parbox{3.5in}
{\vspace{-.1in}
  School of Journalism\\
  University of Missouri\\
  314 Lee Hills Hall\\
  Columbia, MO 65211-1200
}
\parbox{3.5in}
{\vspace{-.1in}
  \faInbox: \email{kearneymw@missouri.edu}\\
  \faHome: \href{http://mikewk.com/}{mikewk.com}\\
  \faGithub: \href{https://github.com/mkearney/}{github.com/mkearney}\\
  \faTwitter: \href{https://twitter.com/kearneymw}{{@}kearneymw}
  %%\faStackOverflow \href{http://stackoverflow.com/users/5435428/mkearney}{{@}mkearney}\\
}
\vspace{.0025in}

\section{Education}
\textbf{Ph.D.}, Communication Studies, University Kansas \hfill 2017
\begin{outerlist}
  \item[] Minor: Social and Behavioral Sciences Methodology
\end{outerlist}
\vspace{.175in}

\textbf{M.A.}, Communication Studies, University Kansas \hfill 2013

\vspace{.15in}

\textbf{B.S.}, Communication, Missouri State University \hfill 2012

\section{Appointments}
Assistant~Professor, University of Missouri \hfill 2017--
\begin{outerlist}
\item[] Journalism Studies, \href{http://journalism.missouri.edu}{School of
    Journalism}
\item[] Data Science \& Analytics, \href{https://dsa.missouri.edu/}{Informatics Institute}
\end{outerlist}
\vspace{.2in}

Instructor, University of Kansas \hfill 2017
\begin{outerlist}
\item[] Leadership Studies, \href{https://ils.ku.edu/about}{Institute
    for Leadership Studies}
\end{outerlist}
\vspace{.2in}
  
Graduate~Assistant, University of Kansas \hfill 2012--2017
\begin{outerlist}
\item[] Research, \href{http://www.crmda.ku.edu/}{Center for Research Methods \&
    Data Analysis}
\item[] Teaching, \href{http://www.coms.ku.edu/}{Communication Studies}
\item[] Debate coach, \href{http://www.debate.ku.edu/}{Kansas Debate Team}
\end{outerlist}

\section{Publications}
\begin{bibenum}
%\item Dietrich, B. J., \& Kearney, M. W. (abstract accepted).
%  When presidential candidates speak social media listens.
%  \emph{Journal of Elections, Public Opinion and Parties}.

\item Kearney, M. W. (In press).
  Analyzing tweets about the 2016 U.S. presidential ``blunder'' election. In Warner,
  Bystrom, McKinney, \& Banwart (Eds.),
  \emph{An unprecedented election: Campaign coverage, communication, and citizens divided}.

\item Banwart, M. C. \&, Kearney, M. W. (In press).
  Social dominance, sexism, and the lasting effects on political communication from the 2016 election. In Warner,
  Bystrom, McKinney, \& Banwart (Eds.),
  \emph{An Unprecedented election: Campaign coverage, communication, and citizens divided}.

\item Kearney, M. W. (2017).
  \href{http://www.tandfonline.com/doi/abs/10.1080/08824096.2016.1250069}{
    Interpersonal goals and political uses of Facebook},
  \emph{Communication Research Reports, 32, 1-9}.
  doi: 10.1080/08824096.2016.1250069

\item[] Kearney, M. W., \& Banwart, M. C. (2017).
  \href{https://books.google.com/books?hl=en&lr=&id=dKc0DgAAQBAJ&oi=fnd&pg=PT73&dq=info:LkhhF-zURiUJ:scholar.google.com&ots=-LyhjqlwlW&sig=9-kgz-wKoIHO6YoIAn2a0Z97O6o#v=onepage&q&f=false}{Methodological
    approaches}. In C. Holtz-Bacha \& M. Just (Eds.), \emph{The
    Routledge handbook of political advertising}. Routledge.

\item[] Kearney, M. W. (2017).
  \href{http://mikewk.com/clpm.pdf}{Cross-lagged panel analysis}.
  In M. Allen (Ed.), \emph{The SAGE encyclopedia of communication
    research methods}.
  Thousand Oaks, CA: Sage.

\item[] Kearney, M. W. (2017).
  \href{http://mikewk.com/cramersv.pdf}{Cram\'{e}r's V}.
  In M. Allen (Ed.), \emph{The SAGE encyclopedia of communication
    research methods}.
  Thousand Oaks, CA: Sage.

\item[] Kearney, M. W. (2017).
  \href{http://mikewk.com/flr.pdf}{Foundational literature reviews}.
  In M. Allen (Ed.), \emph{The SAGE encyclopedia of communication
    research methods}.
  Thousand Oaks, CA: Sage.

\item Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney, M. W. (2015).
  \href{http://www.researchgate.net/publication/269728178_Liking_Obama_and_Romney_(on_Facebook)_An_experimental_evaluation_of_political_engagement_and_efficacy_during_the_2012_general_election}{Liking
    Obama and Romney (on Facebook): An experimental evaluation of
    political engagement and efficacy during the 2012 general
    election}.
  \emph{Computers in Human Behavior, 44}, 279-283.

\item Kearney, M. W. (2014). \href{http://ssrn.com/abstract=2618298}{
    How durable is it? A contextualized interpretation of fiat in
    policy debate}.
  \emph{National Journal of Speech and Debate, 2}, 2-6.

\item[] Kearney, M. W. (2014).
  \href{http://mikewk.com/hndbkchpt.pdf}{Persuading audiences with
    statistical evidence}.
  In C. C. Bird, P. Wagner, \& L. Harroff (Eds.),
  \emph{Speaker-audience communication: The handbook}.
  Boston: Pearson Custom Publishing.
\end{bibenum}

\section{Software}
\begin{bibenum}
\item Kearney, M. W. (2017). newsAPI: R client for newsAPIorg.
  \emph{R package version 0.1.0}. [Computer software]
  \href{https://github.com/mkearney/newsAPI}{https://github.com/mkearney/newsAPI}

\item Kearney, M. W. (2017). nytimes: Interacting with New York Times' APIs.
  \emph{R package version 0.1.0}. [Computer software]
  \href{https://github.com/mkearney/nytimes}{https://github.com/mkearney/nytimes}

\item Kearney, M. W. (2016). rtweet: Collecting Twitter data.
  \emph{R package version 0.4.0}. [Computer software]
  \href{http://cran.r-project.org/package=rtweet}{http://cran.r-project.org/package=rtweet}
\end{bibenum}

\section{Reports}
\begin{bibenum}
\item Kearney, M. W. (2017). \href{https://www.rjionline.org/reporthtml.html}{Trusting {N}ews project report}.
  \emph{Reynolds Journalism Institute}.
\end{bibenum}

\section{Book Reviews}
\begin{bibenum}
\item[] Kearney, M. W. (2014).
  \href{http://ijoc.org/index.php/ijoc/article/view/3405/1280}{Review of
    \emph{Digital currents: How technology and the public are shaping
      TV news} by Rena Bivens}.
  \emph{International Journal of Communication, 8}, 2600-2603.

\item[] Kearney, M. W. (2014).
  \href{http://ijoc.org/index.php/ijoc/article/view/2899/1147}{Review of
    \emph{Foundations and frontiers of deliberative governance} by
    John S. Dryzek with Simon Niemeyer}.
  \emph{International Journal of Communication, 8}, 1540-1543.
\end{bibenum}

%\section{Manuscripts in Progress}
%\begin{bibenum}
%\item Hall, J. A., Kearney, M. W., \& Xing, C. (under review).
%  Two tests of the social displacement hypothesis through social media use.
%\item Muddiman, A., \& Kearney, M. W. Incivility to individuals: An inductive approach to political incivility.
%\item Webb, C. M., \& Kearney, M. W. Statecraft or sacrifice?
%  The domestic political dynamics of economic sanctions.
%\end{bibenum}

\section{Invited Presentations}
\begin{bibenum}
\item[] \href{https://mkearney.github.io/rusersKC}{Twitter data for
    everyone: An introduction to rtweet}. (2017, June). Presentation
  delivered to the R Users Group of Kansas City, Johnson County
  Library.
\item[] Measures of central tendency, dispersion, and some simple
  statistical tests. (2017, March). Presentation delivered on behalf
  of the Center for Research Methods \& Data Analysis to SW 541
  (Social Work Research Seminar).
\item[]
  \href{https://mkearney.github.io/COLLOQUIUM/slides.html#1}{Data
    science and ``big data'' in communication research}. (2017,
  February).  Presentation delivered as part of Spring 2017 colloquium
  series sponsored by Communication Studies Department, University of
  Kansas.
\item[] Working with the NYTimes article search API. (2017, February).
  Presentation delivered as part of Spring 2017 workgroup on \emph{Big
    Dynamic Data}, Center for Research Methods \& Data Analysis,
  University of Kansas.
\item[]
  \href{https://mkearney.github.io/research_talk/pewtalk.html}{Exploring
    new media environments with data science}. (2017,
  January). Presentation delivered to the Pew Research Center,
  Washington, D.C..
\item[] Data wrangling: Parsing JSON, XML, and html data
  structures. (2016, November). Presentation delivered as part of Fall
  2016 workgroup on \emph{Big Dynamic Data}, Center for Research
  Methods \& Data Analysis, University of Kansas.
\item[]
  \href{https://github.com/mkearney/bigdata-workgroup}{Introduction to
    rtweet: Collecting Twitter data}. (2016, November). Presentation
  delivered as part of Fall 2016 workgroup on \emph{Big Dynamic Data},
  Center for Research Methods \& Data Analysis, University of Kansas.
\item[] Data retrieval: Introduction to APIs and web scraping. (2016,
  October). Presentation delivered as part of Fall 2016 workgroup on
  \emph{Big Dynamic Data}, Center for Research Methods \& Data
  Analysis, University of Kansas.
\end{bibenum}

\section{Conference Presentations}
\begin{bibenum}
\item[] Kearney, M. W. (2017, May).
  \href{https://mkearney.github.io/ica17/}{\emph{An introduction to rtweet:
    Collecting Twitter data}}. Paper presented at the 67th Annual
  International Communication Association Convention in San Diego, CA.

\item[] Hall, J. A., Xing, C., \& Kearney, M. W. (2017, May).
  \emph{Two tests of social displacement through social media}.  Paper
  at the 67th Annual International Communication Association
  Convention in San Diego, CA.

\item[] Webb, C. M., \& Kearney, M. W. (2017, February).
  \emph{Statecraft or sacrifice? The domestic political dynamics of
    economic sanctions}. Paper presented at the 58th Annual
  International Studies Association Convention in Baltimore, MD.

\item[] Kearney, M. W. (2016, April). \emph{The null effect of social
    media use on political participation}. Paper presented in the
  Political Communication Interest Group at the CSCA Annual
  Conference, Grand Rapids, MI.

\item[] Kearney, M. W. (2016, April).
  \emph{Bayesian estimation}.
  Panel presented in the Political Communication Interest
  Group at the CSCA Annual Conference, Grand Rapids, MI.

\item[] Kearney, M. W. (2016, April).
  \emph{Theoretical and empirical review of political discussion
    orientation scales}. Paper presented in the Political
  Communication Interest Group at the CSCA Annual Conference, Grand
  Rapids, MI.

\item[] Kearney, M. W., \& Bird, C. C. (2015, November).
  \emph{\#aGreatPlaceToFeelUnsafe: Social media and activism on campus}.
  Panel presented at the NCA 101st Annual Convention, Las Vegas, NV.

\item[] Kearney, M. W. \& Quenette, A. (2015, November).
  \emph{"Nationalizing" the 2014 midterm election:
    Effects of national news source on perceived candidate
    polarization}. Paper presented at the NCA 101st Annual Convention,
  Las Vegas, NV.

\item[] Kearney, M. W. (2015, March).
  \emph{The long game: Political communication and modern longitudinal
    designs}.
  Paper presented at the CSCA Annual Conference, Madison, WI.

\item[] Kearney, M. W. (2015, March).
  \emph{Emphasizing equivalent frames: Political polarization and
    information processing}. Paper presented at the CSCA Annual
  Conference, Madison, WI.\\
  {$\star$} Top paper panel

\item[] Kearney, M. W. (2015, March).
  \emph{Young voters and the polarizing price of political engagement}.
  Paper presented at the CSCA Annual Conference, Madison, WI.

\item[] Kearney, M. W. (2015, March).
  \emph{It's my party: The effects of polarizing party frames on
    information processing}.
  Paper presented at the CSCA Annual Conference, Madison, WI.

\item[] Kearney, M. W. (2014, November).
  \emph{Old arguments, new Face[book]s: Analyzing political
    disagreement on Facebook}.
  Paper presented at the NCA 100th Annual Convention, Chicago, IL.

\item[] Kearney, M. W. (2014, November).
  \emph{Yesterday's public opinion expression, today's status update:
    Interpersonal goals in Facebook political discussion}.
  Paper presented at the NCA 100th Annual Convention, Chicago, IL.

\item[] Kearney, M. W. (2014, May).
  \emph{Agonistic politics and the democratic debate following 9/11}.
  Paper presented at the 16th Biennial RSA Conference, San Antonio,
  TX.

\item[] Kearney, M. W. (2014, March).
  \emph{Civic or civic? An Empirical examination of democratic
    orientations and civic dialogue}.
  Paper presented at the Civic Dialogue and Leadership Conference,
  College Station, TX.

\item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney,
  M. W. (2014, March).
  \emph{The next Facebook election: Evaluating political engagement and
    efficacy on Facebook during the 2012 presidential election}.
  Paper presented at the CSCA Annual Conference, Minneapolis, MN.\\
  {$\star$} Top student paper

\item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney,
  M. W. (2013, November).
  \emph{Finding a role model on Facebook: Political candidates' use of
    Facebook and young women's political engagement}.
  Paper presented at the 99th NCA Annual Convention, Washington, D.C.

\item[] Banwart, M. C., Easley, T. M., Kearney, M. W., Stone, C., \&
  Winfrey, K. W. (2013, November).
  \emph{Dialing in to women... and men? Examining gender in 2012
    debates through RTR research}.
  Panel presented at the 99th NCA Annual Convention, Washington, D.C.
\end{bibenum}

\section{Conference Participation}
\begin{bibenum}
\item[] Chaired panel. (2016, November). \emph{Social media and
    political campaigns: Messages, reactions, and uses of social media
    in the 2016 presidential election}.
  Political Communication Division, NCA 101st Annual Convention,
  Pennsylvania, PA.

\item[] Organized panel. (2016, April). \emph{Updating foundations in
    quantitative research methods}. Political Communication Interest
  Group, CSCA Annual Conference, Grand Rapids, MI.

\item[] Chaired panel. (2016, April). \emph{Cultural identity and
    political influence}.
  Political Communication Interest Group, CSCA Annual Conference,
  Grand Rapids, MI.

\item[] Chaired panel. (2015, November). \emph{Mediated coverage of
    political information}. Political Communication Division, NCA
  101st Annual Convention, Las Vegas, NV.

\item[] Chaired panel. (2014, November). \emph{Partisanship and its
    many effects}. Political Communication Division, NCA 100th Annual
  Convention, Chicago, IL.
\end{bibenum}


\section{Teaching Experience}
\textbf{University of Missouri}
\begin{innerlist}
  \item JOURN 8000: Mass Media Seminar, Instructor \hfill 2017
  \item DTSC 8620: Database and Analytics, Co-Instructor \hfill 2017
    \item[]
\end{innerlist}
\vspace{-.075in}

\textbf{University of Kansas}
\begin{innerlist}
  \item LDST 201: Intro. to Leadership Studies, Instructor \hfill 2017
  \item COMS 307: Intro. to Political Communication, Instructor \hfill 2016
  \item COMS 356: Intro. to Behavioral Research Methods, Instructor \hfill 2015-2016
  \item COMS 201: {[}Online{]} Intro. to Leadership Studies, Instructor \hfill 2014-2015
  \item COMS 343: Seminar in Leadership, Teaching Assistant \hfill 2014
  \item COMS 131: Honors Speaker-Audience Communication, Instructor \hfill 2014
  \item COMS 130: Speaker-Audience Communication, Instructor \hfill 2012-2014
\end{innerlist}
\vspace{-.1in}

\section{Honors \& \hspace{5mm} Awards}
\textbf{Academic Awards}
\begin{innerlist}
  \item Kim Giffin Research Award \hfill 2017
  \item Awarded Honors for Dissertation \hfill 2017
  \item Donn W. Parson Award for Excellence \hfill 2016
  \item Hobb Crockett Departmental Research Award \hfill 2016
  \item Sene and Louella Carlile Scholarship \hfill 2016
  \item Awarded Honors for Comprehensive Examinations \hfill 2015
  \item William A. Conboy Outstanding Graduate Student Award \hfill 2015
  \item Top Paper Panel, CSCA Graduate Student Caucus \hfill 2015
  \item Top Student Paper (co-author), CSCA Political Communication \hfill 2014
  \item Selected Representative, Master's Research Day, Capitol Research Summit \hfill 2014
  \item Awarded Honors for Master's Thesis \hfill 2013
  \item[]
\end{innerlist}
\vspace{-.075in}

\textbf{Debate Awards}
\begin{innerlist}
\item Donn W. Parson Award for Excellence in Coaching \hfill 2013
\item 1st Round At-Large Bid, 3rd Seed, and 4-time qualifier, NDT \hfill 2010
\item Quarterfinalist, 10th speaker, All-American, 4-time elim participant, CEDA \hfill 2010
\end{innerlist}
\vspace{-.075in}

\section{Service}
\textbf{Service to University}
\begin{innerlist}
  \item Meetings with prospective students, Kansas Debate Team \hfill 2012--2015
  \item Associate Director and Assistant Director Jayhawk Debate Institute \hfill 2013--2015
    \begin{outerlist}
    \item[]\textit{In charge of planning, developing, and coordinating the schedule of events,\\
        finances (maintaining a \$250,000 budget), hiring (40+ staff members), and\\
        overall maintenance of the 2-week, 3-week, and incoming-freshman debate \\
        camps (200 plus participants)}.
    \end{outerlist}
  \item[]
\end{innerlist}

\textbf{Service to Department}
\begin{innerlist}
  \item Recruiting, Communication Studies, University of Kansas \hfill 2013--2016
  \item Volunteer, Graduate Student Orientation, University of Kansas \hfill 2013--2016
  \item Faculty representative, Graduate Student Organization \hfill 2015
  \item Secretary/Treasurer, Graduate Student Organization \hfill 2014--2015
  \item Judge, Linkugel Speech Competition, University of Kansas \hfill 2013--2014
  \item[]
\end{innerlist}

\textbf{Service to Discipline}
\begin{innerlist}
\item Journal Reviewer, Western Journal of Communication \hfill 2017
\item Journal Reviewer, Asian Journal of Communication \hfill 2016
\item Member, Committee on Grad Student Involvement, NCA \hfill 2015--2016
  \begin{outerlist}
  \item[]\textit{Organized ad hoc committee on increasing graduate student \\
      involvement in the Political Communication division at NCA}\bigskip
  \end{outerlist}
\item Secretary, Political Communication Interest Group, CSCA \hfill 2015--2016
\item Paper Reviewer, Political Communication Division, NCA \hfill 2014--2015
\item Paper Reviewer, Political Communication Interest Group, CSCA \hfill 2013--2015
\item Social Media Operator, Political Communication Interest Group, CSCA \hfill 2013--2015
\item Local arrangements student volunteer, NCA \hfill 2014
\item Local arrangements student volunteer, CSCA \hfill 2013
\end{innerlist}

\section{References}

Available upon request.

\end{document}

%%% Local Variables:
%%% TeX-engine: luatex
%%% TeX-master: t
%%% End:

