\section{Invited Presentations}
  \begin{bibenum}
%    \item[] TBD talk/workshop on data science tools in R. (2019, February).
%      Talk to be hosted by the Carnegie Melon University Data Science Club in Pittsburgh, PA.
    \item[] \href{https://rtweet-workshop.mikewk.com}{Collecting and Analyzing Twitter Data}. (2018, November).
      Led workshop for the Program In Statistics and Methodology (PRISM) and Political Science Department in Columbus, OH.
    \item[] \href{https://mkearney.github.io/moody_rstats}{Collecting and Analyzing Digital Trace Data}. (2018, October).
      Led workshop for the Moody College of Communication in Austin, TX.
    \item[] \href{https://mkearney.github.io/utchapter/presentation}{Automated accounts in partisan user networks on Twitter}. (2018, April).
      Presentation delivered as part of 2018 New Agendas in Communication series in Austin, TX.
    \item[] \href{https://mkearney.github.io/nicar_tworkshop}{Collecting and analyzing Twitter data}. (2018, April).
      Led workshop for the annual Computer Assisted Reporting Conference in Chicago, IL.
    \item[] \href{https://mkearney.github.io/rusersKC}{Twitter data for everyone: An introduction to rtweet}. (2017, June).
      Presentation delivered to the R Users Group of Kansas City, Johnson County Library.
    \item[] Measures of central tendency, dispersion, and some simple statistical tests. (2017, March).
      Presentation delivered on behalf of the Center for Research Methods \& Data Analysis to SW 541 (Social Work Research Seminar).
    \item[] \href{https://mkearney.github.io/COLLOQUIUM/slides.html}{Data science and ``big data'' in communication research}. (2017, February).
      Presentation delivered as part of Spring 2017 colloquium series sponsored by Communication Studies Department, University of Kansas.
    \item[] Working with the NYTimes article search API. (2017, February).
      Presentation delivered as part of Spring 2017 workgroup on \textit{Big Dynamic Data},
      Center for Research Methods \& Data Analysis, University of Kansas.
    \item[] \href{https://mkearney.github.io/research_talk/pewtalk.html}{Exploring new media environments with data science}. (2017, January).
      Presentation delivered to the Pew Research Center, Washington, D.C..
    \item[] Data wrangling: Parsing JSON, XML, and html data structures. (2016, November).
      Presentation delivered as part of Fall 2016 workgroup on \textit{Big Dynamic Data},
      Center for Research Methods \& Data Analysis, University of Kansas.
    \item[] \href{https://github.com/mkearney/bigdata-workgroup}{Introduction to rtweet: Collecting Twitter data}. (2016, November).
      Presentation delivered as part of Fall 2016 workgroup on \textit{Big Dynamic Data},
      Center for Research Methods \& Data Analysis, University of Kansas.
    \item[] Data retrieval: Introduction to APIs and web scraping. (2016, October).
      Presentation delivered as part of Fall 2016 workgroup on \textit{Big Dynamic Data},
      Center for Research Methods \& Data Analysis, University of Kansas.
  \end{bibenum}
