\section{Media}
  \begin{bibenum}
    \item[] The Maneater (2019, April).
      \href{https://www.themaneater.com/stories/news/mu-researcher-looks-into-political-polarization-lack-of-moderate-voices-on-social-media}{MU researcher looks into political polarization, lack of moderate voices on social media} by Laura Evans
    \item[] 93.9 The Eagle (2019, April).
      \href{https://939theeagle.com/wake-up-columbia-thursday-042519/}{Michael W. Kearney, Ph.D. Assistant Professor Journalism Studies \& Data Science and Analytics talks about his Twitter-politics study} by Branden Rathert.
    \item[] KCUR Central Standard (2019, April).
      \href{https://www.kcur.org/post/seg-1-moderatism-social-media-seg-2-what-are-gs}{Seg. 1: Moderatism \& Social Media | Seg. 2: What Are G's?} by Gina Kaufmann \& Coy Dugger
    \item[] Psych Central (2019, April).
      \href{https://psychcentral.com/news/2019/04/07/moderates-on-twitter-tend-to-be-quieter/144320.html}{Moderates on Twitter Tend to Be Quieter} By Traci Pedersen.
    \item[] Futurity (2019, April).
      \href{https://www.futurity.org/political-polarization-twitter-moderates-2025862/}{Does Twitter make political polarization seem worse?} by Cailin Riley.
    \item[] Phys.org (2019, April).
      \href{https://phys.org/news/2019-04-room-moderates-twitter-voice.html}{The whisper room: Moderates on Twitter are losing their voice} by University of Missouri-Columbia.
    \item[] Outside 2 Std Devs (2019, March).
      \href{https://medium.com/@outside2SDs/a-data-driven-look-at-the-reactions-to-the-mueller-report-186b46e18d02}{A data driven look at the reactions to the Mueller report} byChinmay Shukla \& Mayank Choudhary
    \item[] towardsdatascience (2019, March).
      \href{https://towardsdatascience.com/locating-natural-disasters-through-social-media-feeds-with-r-7c8d3f078750}{Locating Natural Disasters through Social Media Feeds with R} by Chris Kehl
    \item[] The Crosstab (2019, February).
      \href{https://www.thecrosstab.com/2019/02/15/2020-twitter-primary/}{R for Political Data Science Week 7: The 2020 Twitter Primary} by G. Elliott Morris
    \item[] Roll Call (2019, February).
      \href{https://www.rollcall.com/news/lead-midterms-twitter-republicans-went-high-democrats-went-low}{Democrats ‘went low’ on Twitter leading up to 2018} by Aleszu Bajak and Floris Wu.
    \item[] Insider (2018, August).
      \href{https://www.thisisinsider.com/things-that-are-not-helping-your-mental-health-2018-9}{13 things that aren't helping your mental health as much as you think} by Arielle Tschinkel.
    \item[] Revolution Analytics (2018, September).
      \href{http://blog.revolutionanalytics.com/2018/09/anonymous-nyt-op-ed.html}{Who wrote that anonymous NYT op-ed? Text similarity analyses with R}.
    \item[] Vox.com (2018, September).
      \href{https://www.vox.com/mischiefs-of-faction/2018/9/7/17830304/who-wrote-anonymous-white-house-op-ed}{Who wrote the anonymous White House op-ed? A linguistic analysis.} by Julia Azari.
    \item[] VarianceExplained.com (2018, September).
      \href{http://varianceexplained.org/r/op-ed-text-analysis/}{Who wrote the anti-Trump New York Times op-ed? Using tidytext to find document similarity} by David Robinson.
    \item[] Vital Updates (2018, August).
      \href{https://vitalupdates.com/study-sheds-light-on-how-social-media-affects-real-social-situations/}{Study Sheds Light on How Social Media Affects Real Social Situations} by Tori Linville.
    \item[] Data Science {+} (2018, July).
      \href{https://datascienceplus.com/automated-text-feature-engineering-using-textfeatures-in-r/}{Automated Text Feature Engineering using textfeatures in R} by Abdul Majed Raja.
    \item[] TensorFlow for R Blog (2018, January).
      \href{https://blogs.rstudio.com/tensorflow/posts/2018-01-24-analyzing-rtweet-data-with-kerasformula/}{Analyzing rtweet Data with kerasformula} by Pete Mohanty.
    \item[] Guardian (2018, January).
      \href{https://www.theguardian.com/gnm-press-office/2018/jan/26/guardian-us-reaches-milestone-with-over-300000-paying-supporters-in-america}{Guardian US reaches milestone with over 300,000 paying supporters in America}.
    \item[] juliasilge.com (2018, June).
      \href{https://juliasilge.com/blog/punctution-literature/}{Punctuation in literature} by Julia Silge.
    \item[] StudyFinds (2018, August).
      \href{https://www.studyfinds.org/social-media-not-decrease-face-face-interaction-study-says/}{Anti-Social Media? Users Not Having Fewer Face-To-Face Interactions, Study Shows} by Ben Renner.
    \item[] LEO Weekly (2018, January).
      \href{https://www.leoweekly.com/2018/01/kentucky-legislature-twitter-analysis/}{An examination of the Twitter habits of Kentucky lawmakers} by Robert Kahne.
    \item[] Revolution Analytics (2018, March).
      \href{http://blog.revolutionanalytics.com/2018/03/twitter-bot-or-not.html}{BotRNot: An R app to detect Twitter bots}
    \item[] Daily Mail (2018, March).
      \href{http://www.dailymail.co.uk/health/article-5455279/Facebook-does-NOT-decrease-social-interaction.html}{Social media DOESN'T make people isolated and depressed, new research suggests} by J. Baulkman.
    \item[] KOMU (2018, March).
      \href{http://www.komu.com/news/social-media-use-doesn-t-affect-relationships-study-finds}{Social media use doesn't affect relationships, study finds} by M. McDonald.
    \item[] Digital Journal (2018, March).
      \href{http://www.digitaljournal.com/tech-and-science/technology/no-decline-in-face-to-face-interactions-in-the-social-media-era/article/516359}{No decline in face-to-face interactions in the social media era} by T. Sandle.
    \item[] Psych Central (2018, March).
      \href{https://psychcentral.com/news/2018/03/02/social-media-does-not-reduce-social-interactions/133209.html}{Social Media Does Not Reduce Social Interactions} By R. Nauert.
    \item[] Business Services (2018, March).
      \href{http://businessservices24.com/44/no-proof-that-social-media-decrease-face-to-face-interactions/}{No proof that social media decrease face-to-face interactions} by J. Mackey.
    \item[] Futurity (2018, March).
      \href{http://www.futurity.org/social-media-social-interactions-1692872/}{Social media doesn’t hurt your face-to-face socializing} by C. Riley.
    \item[] Missourian (2018, March).
      \href{https://www.columbiamissourian.com/news/higher_education/social-media-doesn-t-affect-our-face-to-face-interactions/}{Social media doesn't affect our face-to-face interactions, study finds} by H. Black.
    \item[] Barron's (2018, March).
      \href{https://www.barrons.com/articles/could-social-media-be-good-for-you-these-researchers-say-yes-1519932207}{Could Social Media Be Good for You? These Researchers Say Yes} by J. Swartz.
    \item[] MU News Bureau (2018, March).
      \href{https://munews.missouri.edu/news-releases/2018/0301-social-media-does-not-decrease-face-to-face-interactions-mu-study-finds/}{Social media does not decrease face-to-face interactions, MU study finds} by C. Riley.
    \item[] MediaPost (2018, February).
      \href{https://mediapost.com/publications/article/315106/social-media-and-human-contact-thrive-together.html}{Social Media And Human Contact Thrive Together} by J. Loechner.
    \item[] Columbia Tribune (2018, February).
      \href{http://www.columbiatribune.com/news/20180217/air-force-officer-discusses-report-on-russian-meddling-at-mu}{Air Force officer discusses report on Russian meddling at MU} by R. Keller.
    \item[] Missourian (2018, February).
      \href{https://www.columbiamissourian.com/news/higher_education/columbia-vulnerable-to-kremlin-fanning-flames-of-protests/article_929cf366-11ad-11e8-9631-63ac0b4a6fd3.html}{Columbia vulnerable to Kremlin fanning flames of 2015 protests} by E. McKinley.
    \item[] Politico (2018, January).
      \href{https://www.politico.com/amp/story/2018/02/06/gop-republican-voters-media-bias-trusted-sites-393650}{ GOP voters trust CNN, N.Y. Times over Breitbart, InfoWars} by J. Schwartz.
    \item[] Wired (2018, January).
      \href{https://www.wired.com/story/you-cant-trust-facebooks-search-for-trusted-news/}{You can't trust Facebook's search for trusted news} by A. Rogers.
    \item[] Fortune (2018, January).
      \href{http://fortune.com/2018/01/21/new-york-times-stock-facebooks-trusted-news/}{New York Times Stock Surges After Facebook's 'Trusted News' Announcement} by D. Morris.
    \item[] The Atlantic (2018, January).
      \href{https://www.theatlantic.com/technology/archive/2018/01/facebook-media-trustworthiness/551045/}{5 Questions About Facebook's Plan to Rate Media by 'Trustworthiness'} by A. Madrigal.
    \item[] CNET (2018, January).
      \href{https://www.cnet.com/news/with-two-questions-facebook-is-deciding-the-future-of-news-zuckerberg-fake-news/}{With two questions Facebook is deciding the future of news} by I. Sherr.
    \item[] AdWeek (2017, August).
      \href{http://www.adweek.com/tvnewser/how-a-british-tv-network-became-one-of-the-most-trusted-news-sources-among-americans/339872}{How A British TV Network Became One of the Most Trusted News Sources Among Americans} by A. J. Katz.
    \item[] MarketWatch (2017, August).
      \href{https://www.marketwatch.com/story/these-are-the-most-and-the-least-trusted-news-sources-in-the-us-2017-08-03}{These are the most — and the least — trusted news sources in the U.S.} by S. Chang.
    \item[] O'Dwyer's (2017, August).
      \href{http://www.odwyerpr.com/story/public/9210/2017-08-08/internet-news-sites-seen-as-least-trustworthy.html}{Internet News Sites Seen as Least Trustworthy} By J. Gingerich.
    \item[] The Guardian(2017, August).
      \href{https://www.theguardian.com/media/2017/aug/09/four-uk-news-sources-among-top-10-most-trusted-in-us-survey}{Four UK news sources among top 10 most trusted in US – survey} by G. Ruddick.
    \item[] The Wrap (2017, August).
      \href{https://www.thewrap.com/british-media-outlets-most-trusted-us-news-sources-in-new-poll/}{British Media Outlets Most Trusted US News Sources in New Poll} by B. Flood.
    \item[] The Drum (2017, August).
      \href{http://www.thedrum.com/news/2017/08/08/buzzfeed-and-breitbart-bottom-media-trust-list-americans-place-trust-british-outlets}{BuzzFeed and Breitbart at bottom of media trust list as Americans place trust in British outlets} by J. Glenday.
  \end{bibenum}
