\section{Software}

  \textbf{CRAN packages}
    \begin{innerlist}
      \item pkgverse: Build a Meta-Package Universe. \textit{R package}. \href{http://cran.r-project.org/package=pkgverse}{\faExternalLink}
      \item tbltools: Tools for Working with Tibbles. \textit{R package}. \href{http://cran.r-project.org/package=tbltools}{\faExternalLink}
      \item tfse: Tools for Script Editing. \textit{R package}. \href{http://cran.r-project.org/package=tfse}{\faExternalLink}
      \item funique: A Faster Unique Function. \textit{R package}. \href{http://cran.r-project.org/package=funique}{\faExternalLink}
      \item textfeatures: Extracts Features from Text. \textit{R package}. \href{http://cran.r-project.org/package=textfeatures}{\faExternalLink}
      \item rtweet: Collecting Twitter data. \textit{R package}. \href{http://cran.r-project.org/package=rtweet}{\faExternalLink}
    \end{innerlist}\vspace{1em}

  \textbf{Github packages}
    \begin{innerlist}
      \item tweetbotornot: Bot detection. \textit{R package}. \href{https://github.com/mkearney/tweetbotornot}{\faExternalLink}
    %  \item getwebdata: Importing web data. \textit{R package}. \href{https://github.com/mkearney/getwebdata}{\faExternalLink}
      \item kaggler: Client for accessing Kaggle’s API. \textit{R package}. \href{https://github.com/mkearney/kaggler}{\faExternalLink}
    %  \item wordword: Simple little thesaurus package. \textit{R package}. \href{https://github.com/mkearney/wordword}{\faExternalLink}
      \item ig: Client for accessing Instagram's API. \textit{R package}. \href{https://github.com/mkearney/ig}{\faExternalLink}
    %  \item name2sex: SSA sex proportions. \textit{R package}. \href{https://github.com/mkearney/name2sex}{\faExternalLink}
    %  \item chr: Simple string manipulation. \textit{R package}. \href{https://github.com/mkearney/chr}{\faExternalLink}
      \item newsAPI: R client for newsAPIorg. \textit{R package}. \href{https://github.com/mkearney/newsAPI}{\faExternalLink}
      \item nytimes: Interacting with NYTimes APIs. \textit{R package}. \href{https://github.com/mkearney/nytimes}{\faExternalLink}
    \end{innerlist}\vspace{1em}

  \textbf{Web Apps}
    \begin{innerlist}
      \item tweetbotornot: Bot detection. \textit{Shiny App}. \href{https://mikewk.shinyapps.io/botornot/}{\faExternalLink}
      \item Interactive Friendship Tool. \textit{Shiny App}. \href{https://mikewk.shinyapps.io/friendship/}{\faExternalLink}
      \item Simple tool for visualizing correlations. \textit{Shiny App}. \href{https://mikewk.shinyapps.io/correlation/}{\faExternalLink}
    \end{innerlist}
