\documentclass[11pt,letterpaper]{article}
\input{tex/preamble}

\begin{document}

\input{tex/heading}

\section{Education}
\textbf{Ph.D.}, Communication Studies, University Kansas \hfill 2017
  \begin{outerlist}
    \item[] Minor: Social and Behavioral Sciences Methodology
  \end{outerlist} \vspace{.175in}

\textbf{M.A.}, Communication Studies, University Kansas \hfill 2013

\vspace{.15in}

\textbf{B.S.}, Communication, Missouri State University \hfill 2012

\section{Appointments}
Assistant~Professor, University of Missouri \hfill 2017--
  \begin{outerlist}
    \item[] Journalism Studies, \href{http://journalism.missouri.edu}{School of Journalism}
    \item[] Data Science \& Analytics, \href{https://muii.missouri.edu/}{Informatics Institute}
  \end{outerlist}\vspace{.2in}

Instructor, University of Kansas \hfill 2017
  \begin{outerlist}
    \item[] Leadership Studies, \href{https://ils.ku.edu/about}{Institute for Leadership Studies}
  \end{outerlist}\vspace{.2in}

Graduate~Assistant, University of Kansas \hfill 2012--2017
  \begin{outerlist}
    \item[] Research, \href{http://www.crmda.ku.edu/}{Center for Research Methods \& Data Analysis}
    \item[] Teaching, \href{http://www.coms.ku.edu/}{Communication Studies}
    \item[] Debate coach, \href{http://www.debate.ku.edu/}{Kansas Debate Team}
  \end{outerlist}

\section{Publications}
  \begin{bibenum}
    \item Hall, J. A., Kearney, M. W., \& Xing, C. (2018).
    Two tests of social displacement through social media use.
    \textit{Information, Communication and Society}.
    \href{https://doi.org/10.1080/1369118X.2018.1430162}{10.1080/1369118X.2018.1430162}

    \item Kearney, M. W. (2018).
    Analyzing tweets about the 2016 U.S. presidential ``blunder'' election.
    In B. R. Warner, D. G. Bystrom, M. S. McKinney, \& M. Banwart (Eds.),
    \textit{An unprecedented election: Campaign Coverage, Communication, and Citizens Divided}.
    \href{http://publisher.abc-clio.com/9781440860669/390}{9781440860669/390}

    \item Banwart, M. C. \&, Kearney, M. W. (2018).
    Social dominance, sexism, and the lasting effects on political communication from the 2016 election. In B. R. Warner,
    D. G. Bystrom, M. S. McKinney, \& M. Banwart (Eds.),
    \textit{An Unprecedented Election: Campaign Coverage, Communication, and Citizens Divided}.
    \href{http://publisher.abc-clio.com/9781440860669/426}{9781440860669/426}

    \item Kearney, M. W. (2017).
    \href{http://www.tandfonline.com/doi/abs/10.1080/08824096.2016.1250069}{Interpersonal goals and political uses of Facebook},
    \textit{Communication Research Reports, 32, 1-9}.
    \href{https://doi.org/10.1080/08824096.2016.1250069}{10.1080/08824096.2016.1250069}

    \item[] Kearney, M. W., \& Banwart, M. C. (2017).
    Methodological approaches.
    In C. Holtz-Bacha \& M. Just (Eds.), \textit{Routledge Handbook of Political Advertising} (29-37).
    \href{https://www.routledgehandbooks.com/doi/10.4324/9781315694504.ch3}{10.4324/9781315694504.ch3}

    \item[] Kearney, M. W. (2017).
    \href{http://mikewk.com/clpm.pdf}{Cross-lagged panel analysis}.
    In M. Allen (Ed.), \textit{SAGE Encyclopedia of Communication Research Methods} (313-314).
    \href{http://dx.doi.org/10.4135/9781483381411.n117}{10.4135/9781483381411.n117}

    \item[] Kearney, M. W. (2017).
    \href{http://mikewk.com/cramersv.pdf}{Cram\'{e}r's V}.
    In M. Allen (Ed.), \textit{SAGE Encyclopedia of Communication Research Methods} (290).
    \href{http://dx.doi.org/10.4135/9781483381411.n107}{10.4135/9781483381411.n107}

    \item[] Kearney, M. W. (2017).
    \href{http://mikewk.com/flr.pdf}{Foundational literature reviews}.
    In M. Allen (Ed.), \textit{SAGE Encyclopedia of Communication Research Methods} (878-880).
    \href{http://dx.doi.org/10.4135/9781483381411.n304}{10.4135/9781483381411.n304}

    \item Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney, M. W. (2015).
    \href{http://www.researchgate.net/publication/269728178_Liking_Obama_and_Romney_(on_Facebook)_An_experimental_evaluation_of_political_engagement_and_efficacy_during_the_2012_general_election}{
    Liking Obama and Romney (on Facebook): An experimental evaluation of political engagement and efficacy during the 2012 general election}.
    \textit{Computers in Human Behavior, 44}, 279-283.
    \href{https://doi.org/10.1016/j.chb.2014.11.032}{10.1016/j.chb.2014.11.032}

    \item Kearney, M. W. (2014). \href{http://ssrn.com/abstract=2618298}{
    How durable is it? A contextualized interpretation of fiat in policy debate}.
    \textit{National Journal of Speech and Debate, 2}, 2-6.
    \href{http://hdl.handle.net/1808/15009}{hdl.handle.net/1808/15009}

    \item[] Kearney, M. W. (2014). Persuading audiences with statistical evidence.
    In C. C. Bird, P. Wagner, \& L. Harroff (Eds.), \textit{Speaker-audience communication: The handbook}.
    Boston: Pearson Custom Publishing.
    \href{https://dx.doi.org/10.13140/RG.2.2.27930.34242}{10.13140/RG.2.2.27930.34242}
  \end{bibenum}

\section{Software}
  \begin{bibenum}
    \item Kearney, M. W. (2017). newsAPI: R client for newsAPIorg.
    \textit{R package version 0.1.0}. [Computer software]
    \href{https://github.com/mkearney/newsAPI}{https://github.com/mkearney/newsAPI}

    \item Kearney, M. W. (2017). nytimes: Interacting with New York Times' APIs.
    \textit{R package version 0.1.0}. [Computer software]
    \href{https://github.com/mkearney/nytimes}{https://github.com/mkearney/nytimes}

    \item Kearney, M. W. (2016). rtweet: Collecting Twitter data.
    \textit{R package version 0.4.0}. [Computer software]
    \href{http://cran.r-project.org/package=rtweet}{http://cran.r-project.org/package=rtweet}
  \end{bibenum}

\section{Reports}
  \begin{bibenum}
    \item Kearney, M. W. (2017). \href{https://www.rjionline.org/reporthtml.html}{Trusting {N}ews project report}.
    \textit{Reynolds Journalism Institute}.
  \end{bibenum}

\section{Book Reviews}
  \begin{bibenum}
    \item[] Kearney, M. W. (2014).
    \href{http://ijoc.org/index.php/ijoc/article/view/3405/1280}{Review of
    \textit{Digital currents: How technology and the public are shaping TV news} by Rena Bivens}.
    \textit{International Journal of Communication, 8}, 2600-2603.

    \item[] Kearney, M. W. (2014).
    \href{http://ijoc.org/index.php/ijoc/article/view/2899/1147}{Review of
    \textit{Foundations and frontiers of deliberative governance} by John S. Dryzek with Simon Niemeyer}.
    \textit{International Journal of Communication, 8}, 1540-1543.
  \end{bibenum}

\section{Invited Presentations}
  \begin{bibenum}
    \item[] Collecting and analyzing Twitter data. (2018, April). Workshop
      to be directed at the annual Computer Assisted Reporting Conference
      in Chicago, IL.
    \item[] \href{https://mkearney.github.io/rusersKC}{Twitter data for
      everyone: An introduction to rtweet}. (2017, June). Presentation
      delivered to the R Users Group of Kansas City, Johnson County
      Library.
    \item[] Measures of central tendency, dispersion, and some simple
      statistical tests. (2017, March). Presentation delivered on behalf
      of the Center for Research Methods \& Data Analysis to SW 541
      (Social Work Research Seminar).
    \item[]
      \href{https://mkearney.github.io/COLLOQUIUM/slides.html}{Data
      science and ``big data'' in communication research}. (2017,
      February).  Presentation delivered as part of Spring 2017 colloquium
      series sponsored by Communication Studies Department, University of
      Kansas.
    \item[] Working with the NYTimes article search API. (2017, February).
      Presentation delivered as part of Spring 2017 workgroup on \textit{Big
      Dynamic Data}, Center for Research Methods \& Data Analysis,
      University of Kansas.
    \item[]
      \href{https://mkearney.github.io/research_talk/pewtalk.html}{Exploring
      new media environments with data science}. (2017,
      January). Presentation delivered to the Pew Research Center,
      Washington, D.C..
    \item[] Data wrangling: Parsing JSON, XML, and html data
      structures. (2016, November). Presentation delivered as part of Fall
      2016 workgroup on \textit{Big Dynamic Data}, Center for Research
      Methods \& Data Analysis, University of Kansas.
    \item[]
      \href{https://github.com/mkearney/bigdata-workgroup}{Introduction to
      rtweet: Collecting Twitter data}. (2016, November). Presentation
      delivered as part of Fall 2016 workgroup on \textit{Big Dynamic Data},
      Center for Research Methods \& Data Analysis, University of Kansas.
    \item[] Data retrieval: Introduction to APIs and web scraping. (2016,
      October). Presentation delivered as part of Fall 2016 workgroup on
      \textit{Big Dynamic Data}, Center for Research Methods \& Data
      Analysis, University of Kansas.
  \end{bibenum}

\section{Conference Presentations}
  \begin{bibenum}
    \item[] Kearney, M.W. (2018, May). \textit{A network-based approach to
      estimating political partisanship}. Paper accepted for the the
      68th Annual International Communication Association conference in
      Prague, Czech Republic.

    \item[] Hall, J. A., Kearney, M. W., \& Xing, C. (2017,
      May). \textit{Two tests of social displacement through social media
      use}. Paper presented at the 67th Annual International
      Communication Association Convention in San Diego, CA.

    \item[] Warner, B. R., \& Kearney, M. W. (2017, Sep). \textit{No
      spillover: A longitudinal analysis of the effects of political
      communication online and off}. Paper presented at the 3rd Annual
      International Journal of Press/Politics Conference in Oxford, UK.

    \item[] Kearney, M. W., \& Webb, C. M. (2017, Sep). \textit{\#Politics:
      Using Twitter data to study public attitudes and public attention
      in event}. Paper presented at the 113th Annual American Political
      Science Association Meeting \& Exhibition in San Fransico, CA.

    \item[] Kearney, M. W. (2017, May).
      \href{https://mkearney.github.io/ica17/}{\textit{An introduction to rtweet:
      Collecting Twitter data}}. Paper presented at the 67th Annual
      International Communication Association Convention in San Diego, CA.

    \item[] Hall, J. A., Xing, C., \& Kearney, M. W. (2017, May).
      \textit{Two tests of social displacement through social media}.
      Paper presented at the 67th Annual International Communication Association
      Convention in San Diego, CA.

    \item[] Webb, C. M., \& Kearney, M. W. (2017, February).
      \textit{Statecraft or sacrifice? The domestic political dynamics of
      economic sanctions}. Paper presented at the 58th Annual
      International Studies Association Convention in Baltimore, MD.

    \item[] Kearney, M. W. (2016, April). \textit{The null effect of social
      media use on political participation}. Paper presented in the
      Political Communication Interest Group at the CSCA Annual
      Conference, Grand Rapids, MI.

    \item[] Kearney, M. W. (2016, April).
      \textit{Bayesian estimation}.
      Panel presented in the Political Communication Interest
      Group at the CSCA Annual Conference, Grand Rapids, MI.

    \item[] Kearney, M. W. (2016, April).
      \textit{Theoretical and empirical review of political discussion
      orientation scales}. Paper presented in the Political
      Communication Interest Group at the CSCA Annual Conference, Grand
      Rapids, MI.

    \item[] Kearney, M. W., \& Bird, C. C. (2015, November).
      \textit{\#aGreatPlaceToFeelUnsafe: Social media and activism on campus}.
      Panel presented at the NCA 101st Annual Convention, Las Vegas, NV.

    \item[] Kearney, M. W. \& Quenette, A. (2015, November).
      \textit{"Nationalizing" the 2014 midterm election:
      Effects of national news source on perceived candidate
      polarization}. Paper presented at the NCA 101st Annual Convention,
      Las Vegas, NV.

    \item[] Kearney, M. W. (2015, March).
      \textit{The long game: Political communication and modern longitudinal
      designs}.
      Paper presented at the CSCA Annual Conference, Madison, WI.

    \item[] Kearney, M. W. (2015, March).
      \textit{Emphasizing equivalent frames: Political polarization and
      information processing}. Paper presented at the CSCA Annual
      Conference, Madison, WI.\\
      {$\star$} Top paper panel

    \item[] Kearney, M. W. (2015, March).
      \textit{Young voters and the polarizing price of political engagement}.
      Paper presented at the CSCA Annual Conference, Madison, WI.

    \item[] Kearney, M. W. (2015, March).
      \textit{It's my party: The effects of polarizing party frames on
      information processing}.
      Paper presented at the CSCA Annual Conference, Madison, WI.

    \item[] Kearney, M. W. (2014, November).
      \textit{Old arguments, new Face[book]s: Analyzing political
      disagreement on Facebook}.
      Paper presented at the NCA 100th Annual Convention, Chicago, IL.

    \item[] Kearney, M. W. (2014, November).
      \textit{Yesterday's public opinion expression, today's status update:
      Interpersonal goals in Facebook political discussion}.
      Paper presented at the NCA 100th Annual Convention, Chicago, IL.

    \item[] Kearney, M. W. (2014, May).
      \textit{Agonistic politics and the democratic debate following 9/11}.
      Paper presented at the 16th Biennial RSA Conference, San Antonio,
      TX.

    \item[] Kearney, M. W. (2014, March).
      \textit{Civic or civic? An Empirical examination of democratic
      orientations and civic dialogue}.
      Paper presented at the Civic Dialogue and Leadership Conference,
      College Station, TX.

    \item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney,
      M. W. (2014, March).
      \textit{The next Facebook election: Evaluating political engagement and
      efficacy on Facebook during the 2012 presidential election}.
      Paper presented at the CSCA Annual Conference, Minneapolis, MN.\\
      {$\star$} Top student paper

    \item[] Pennington, N. R., Winfrey, K. L., Warner, B. R., \& Kearney,
      M. W. (2013, November).
      \textit{Finding a role model on Facebook: Political candidates' use of
      Facebook and young women's political engagement}.
      Paper presented at the 99th NCA Annual Convention, Washington, D.C.

    \item[] Banwart, M. C., Easley, T. M., Kearney, M. W., Stone, C., \&
      Winfrey, K. W. (2013, November).
      \textit{Dialing in to women... and men? Examining gender in 2012
      debates through RTR research}.
      Panel presented at the 99th NCA Annual Convention, Washington, D.C.
  \end{bibenum}

\section{Conference Participation}
  \begin{bibenum}
    \item[] Chaired panel. (2016, November). \textit{Social media and
      political campaigns: Messages, reactions, and uses of social media
      in the 2016 presidential election}.
      Political Communication Division, NCA 101st Annual Convention,
      Pennsylvania, PA.

    \item[] Organized panel. (2016, April). \textit{Updating foundations in
      quantitative research methods}. Political Communication Interest
      Group, CSCA Annual Conference, Grand Rapids, MI.

    \item[] Chaired panel. (2016, April). \textit{Cultural identity and
      political influence}.
      Political Communication Interest Group, CSCA Annual Conference,
      Grand Rapids, MI.

    \item[] Chaired panel. (2015, November). \textit{Mediated coverage of
      political information}. Political Communication Division, NCA
      101st Annual Convention, Las Vegas, NV.

    \item[] Chaired panel. (2014, November). \textit{Partisanship and its
      many effects}. Political Communication Division, NCA 100th Annual
      Convention, Chicago, IL.
  \end{bibenum}

\section{Teaching Experience}
\textbf{University of Missouri}
\begin{innerlist}
  \item JOURN 8006: Quantitative Research Methods in Journalism \hfill 2018
  \item JOURN 8000: Mass Media Seminar \hfill 2017
  \item DATA\_SCI 8801: Advanced Topics: Streaming Social Media Data \hfill 2018
  \item DATA\_SCI 8610: Statistical and Mathematical Foundations for Data Analytics \hfill 2017
    \item[]
\end{innerlist}
\vspace{-.075in}

\textbf{University of Kansas}
\begin{innerlist}
  \item LDST 201: Intro. to Leadership Studies \hfill 2017
  \item COMS 307: Intro. to Political Communication \hfill 2016
  \item COMS 356: Intro. to Behavioral Research Methods \hfill 2015-2016
  \item COMS 201: {[}Online{]} Intro. to Leadership Studies \hfill 2014-2015
  \item COMS 343: Seminar in Leadership (Teaching Assistant) \hfill 2014
  \item COMS 131: Honors Speaker-Audience Communication \hfill 2014
  \item COMS 130: Speaker-Audience Communication \hfill 2012-2014
\end{innerlist}
\vspace{-.1in}

\section{Honors \& \hspace{5mm} Awards}
\textbf{Academic Awards}
\begin{innerlist}
  \item Lynda Lee Kaid Outstanding Dissertation Award, NCA \hfill 2017
  \item Kim Giffin Research Award, University of Kansas \hfill 2017
  \item Awarded Honors for Dissertation, University of Kansas \hfill 2017
  \item Donn W. Parson Award for Excellence, University of Kansas \hfill 2016
  \item Hobb Crockett Departmental Research Award, University of Kansas \hfill 2016
  \item Sene and Louella Carlile Scholarship, University of Kansas \hfill 2016
  \item Awarded Honors for Comprehensive Examinations, University of Kansas \hfill 2015
  \item William A. Conboy Outstanding Graduate Student Award, University of Kansas \hfill 2015
  \item Top Paper Panel, CSCA Graduate Student Caucus \hfill 2015
  \item Top Student Paper (co-author), CSCA Political Communication \hfill 2014
  \item Selected Representative, Master's Research Day, Capitol Research Summit \hfill 2014
  \item Awarded Honors for Master's Thesis, University of Kansas \hfill 2013
  \item[]
\end{innerlist}
\vspace{-.075in}

\textbf{Debate Awards}
\begin{innerlist}
\item Donn W. Parson Award for Excellence in Coaching \hfill 2013
\item 1st Round At-Large Bid, 3rd Seed, and 4-time qualifier, NDT \hfill 2010
\item Quarterfinalist, 10th speaker, All-American, 4-time elim participant, CEDA \hfill 2010
\end{innerlist}
\vspace{-.075in}

\section{Editing \& Reviewing}
\textbf{Editorial Board}
\begin{innerlist}
  \item Western Journal of Communication \hfill 2017--
  \item[]
\end{innerlist}
\vspace{-.075in}

\textbf{Ad Hoc Reviewer}
\begin{innerlist}
  \item Journalism \& Mass Communication Quarterly \hfill 2017
  \item Western Journal of Communication \hfill 2017
  \item Asian Journal of Communication \hfill 2016
\end{innerlist}
\vspace{-.075in}

\section{Service}
\textbf{Service to School}
\begin{innerlist}
  \item Member, Committee on Innovation, University of Missouri \hfill 2017--2018
  \item Recruiting, Communication Studies, University of Kansas \hfill 2013--2016
  \item Volunteer, Graduate Student Orientation, University of Kansas \hfill 2013--2016
  \item Faculty representative, Graduate Student Organization \hfill 2015
  \item Secretary/Treasurer, Graduate Student Organization \hfill 2014--2015
  \item Meetings with prospective students, Kansas Debate Team \hfill 2012--2015
  \item Associate Director and Assistant Director Jayhawk Debate Institute \hfill 2013--2015
    \begin{outerlist}
    \item[]\textit{In charge of planning, developing, and coordinating the schedule of events,\\
        finances (maintaining a \$250,000 budget), hiring (40+ staff members), and\\
        overall maintenance of the 2-week, 3-week, and incoming-freshman debate \\
        camps (200 plus participants)}.
    \end{outerlist}
   \vspace{1em}
  \item Judge, Linkugel Speech Competition, University of Kansas \hfill 2013--2014
  \item[]
\end{innerlist}

\textbf{Service to Discipline}
\begin{innerlist}
  \item Paper Reviewer, Political Communication Division, ICA \hfill 2017--2018
  \item Member, Committee on Grad Student Involvement, NCA \hfill 2015--2016
  \begin{outerlist}
    \item[]\textit{Organized ad hoc committee on increasing graduate student \\
      involvement in the Political Communication division at NCA}\bigskip
  \end{outerlist}
  \item Secretary, Political Communication Interest Group, CSCA \hfill 2015--2016
  \item Paper Reviewer, Political Communication Division, NCA \hfill 2014--2015
  \item Paper Reviewer, Political Communication Interest Group, CSCA \hfill 2013--2015
  \item Social Media Operator, Political Communication Interest Group, CSCA \hfill 2013--2015
  \item Local arrangements student volunteer, NCA \hfill 2014
  \item Local arrangements student volunteer, CSCA \hfill 2013
\end{innerlist}

\section{Media}
  \begin{bibenum}
    \item[] Barron's (2018, March).
    \href{https://www.barrons.com/articles/could-social-media-be-good-for-you-these-researchers-say-yes-1519932207}{Could Social Media Be Good for You? These Researchers Say Yes} by J Swartz.

    \item[] MU News Bureau (2018, March).
    \href{https://munews.missouri.edu/news-releases/2018/0301-social-media-does-not-decrease-face-to-face-interactions-mu-study-finds/}{Social media does not decrease face-to-face interactions, MU study finds} by C. Riley.

    \item[] MediaPost (2018, February).
    \href{https://mediapost.com/publications/article/315106/social-media-and-human-contact-thrive-together.html}{Social Media And Human Contact Thrive Together} by Jack Loechner.

    \item[] Columbia Tribune (2018, February).
    \href{http://www.columbiatribune.com/news/20180217/air-force-officer-discusses-report-on-russian-meddling-at-mu}{Air Force officer discusses report on Russian meddling at MU} by R. Keller.

    \item[] Missourian (2018, February).
    \href{https://www.columbiamissourian.com/news/higher_education/columbia-vulnerable-to-kremlin-fanning-flames-of-protests/article_929cf366-11ad-11e8-9631-63ac0b4a6fd3.html}{Columbia vulnerable to Kremlin fanning flames of 2015 protests} by E. McKinley.

    \item[] Politico (2018, January).
    \href{https://www.politico.com/amp/story/2018/02/06/gop-republican-voters-media-bias-trusted-sites-393650}{ GOP voters trust CNN, N.Y. Times over Breitbart, InfoWars} by J. Schwartz.

  \item[] Wired (2018, January).
    \href{https://www.wired.com/story/you-cant-trust-facebooks-search-for-trusted-news/}{You
      can't trust Facebook's search for trusted news} by A. Rogers.

    \item[] CNET (2018, January).
  \href{https://www.cnet.com/news/with-two-questions-facebook-is-deciding-the-future-of-news-zuckerberg-fake-news/}{With
    two questions Facebook is deciding the future of news} by I. Sherr.

  \end{bibenum}

\end{document}
